Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The interaction between embedded software and physical processes created a different class of systems, which are complex, highly integrated, and present a mixture of continuous and discrete dynamics, named as \textit{hybrid systems} (HSs). Indeed, the embedded-system domain allied to the most recent communication revolution caused an intense integration between different and spread physical processes, which are called embedded \& cyber-physical systems (ECPSs). The presence of modern communication technologies ({\it e.g.}, internet of things - IoT) causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found in the embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging ECPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a ECPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

Figure~\ref{intelligent-product} shows some examples of embedded systems, which typically consist of a human-machine interface ({\it e.g.}, keyboard and display), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) \cite{Kopetz11}. Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even many aspects of their lives, with serious consequences. On the one hand, portable embedded systems are capable of monitoring and identifying conditions that are very difficult for a physician, mainly when his contact with patients happens only in medical clinics. On the other hand, wrong or incomplete diagnostic data may delay necessary treatments or deteriorate patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.4]{figure1.jpg}
	\caption{An embedded system is part of a well-specified larger one (intelligent product).}
	\label{intelligent-product}
\end{figure}

Besides, when physical interaction with the real world is needed, which happens in ECPSs, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to synthesize a given particular system, by ensuring that all needed functions are correctly implemented and the correct behavior is exhibited, {i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

@@

Regarding behavior correctness, one important observation is that it is becoming more difficult, since fixed mathematical models are being replaced by machine learning approaches (ML) \cite{mlembe}, where future operation may change based on data acquired during previous actions, due to model updating. As a consequence, system-correctness verification procedures should also adapt somehow and incorporate new checks, which may also rely on ML, when analyzing target models or fed with acquired data.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency)~\cite{Kroening15} or even new structures provided with the goal of ensuring more computational capacity~\cite{cudalucas} must be considered during verification. Such observations expand the addressed issues and even complement what was mentioned in the previous paragraphs.

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, counter-example guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} then describes current achievements and future trends in verification and synthesis of embedded \& cyber-physical systems and Section \ref{Newapp} addresses new applications, which take into account the new trends mentioned here. Finally, we conclude and describe future work in Section~\ref{conclusions}.

>>>>

The interaction between embedded software and physical processes created a different class of systems, which are complex, highly integrated, and present a mixture of continuous and discrete dynamics, named as \textit{hybrid systems} (HSs). Indeed, the embedded-system domain allied to the most recent communication revolution caused an intense integration between different and spread physical processes, which are called embedded \& cyber-physical systems (ECPSs). In particular, the presence of modern communication technologies ({\it e.g.}, internet of things - IoT) causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found in the embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging ECPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a ECPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

Figure~\ref{intelligent-product} shows some examples of ECPS, which typically consist of a human-machine interface ({\it e.g.}, keyboard and display), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) that can be connected to some physical plant~\cite{Kopetz11}. Indeed, many current ECPS, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even many aspects of their lives, with serious consequences. On the one hand, portable ECPS are capable of monitoring and identifying conditions that are very difficult for a physician, mainly when his contact with patients happens only in medical clinics. On the other hand, wrong or incomplete diagnostic data may delay necessary treatments or deteriorate patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.4]{figure1.jpg}
	\caption{An embedded system is part of a well-specified larger one (intelligent product).}
	\label{intelligent-product}
\end{figure}

Besides, when physical interaction with the real world is needed, which happens in ECPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to synthesize a given particular system, by ensuring that all needed functions are correctly implemented and the correct behavior is exhibited, {\it i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

@@

Regarding behavior correctness, one important observation is that it is becoming more difficult, since fixed mathematical models are being replaced by machine learning approaches (ML) \cite{mlembe}, where future operation may change based on data acquired during previous actions, due to model updating. As a consequence, system-correctness verification procedures should also adapt somehow and incorporate new checks, which may also rely on ML, when analyzing target models or fed with acquired data, as recently reported in the literature~\cite{DBLP:conf/cav/HuangKWW17,DBLP:conf/cav/KatzBDJK17}, where formal verification techniques are applied to verify deep neural networks.

A number of distinctive characteristics might influence the ECPS verification and synthesis process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency)~\cite{Kroening15} or even new structures provided with the goal of ensuring more computational capacity~\cite{cudalucas} must be considered during verification. Such observations expand the addressed issues and even complement what was mentioned previously.

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, Craig interpolants, counterexample guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} then describes current achievements and future trends in verification and synthesis of ECPS and Section \ref{Newapp} addresses new applications, which take into account the new trends ({\it e.g.}, ML) mentioned here. Finally, we conclude and describe future work in Section~\ref{conclusions}.
